msmsTests package\\ Blocks design to compensate batch effects

### 2013-09-27 inst/doc/msmsTests-Vignette.Rnw
use hyperref LaTeX package so vignette will build on Linux and Mac
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/msmsTests@79450 bc3139a8-67e5-0310-9ffc-ced21a209358
In function test.results(), DEP column changed to logical
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/msmsTests@80847 bc3139a8-67e5-0310-9ffc-ced21a209358

\title{msmsTests package\\
       LC-MS/MS post test filters to improve reproducibility}
\author{Josep Gregori, Alex Sanchez, and Josep Villanueva\\
   Vall Hebron Institute of Oncology \&\\
   Statistics Dept. Barcelona University\\
  \texttt{jgregori@vhio.net}}
\date{July 2013}

@@

###  Relevant proteins according to the Poisson GLM
pois.tbl <- test.results(pois.res,e,pData(e)$treat,"U600","U200",div,
                         alpha=alpha.cut,minSpC=SpC.cut,minLFC=lFC.cut,
                         method="BH")$tres
(pois.nms <- rownames(pois.tbl)[pois.tbl$DEP=="T"])

@@

###  Relevant proteins according to the quasi-likelihood GLM
ql.tbl <- test.results(ql.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
(ql.nms <- rownames(ql.tbl)[ql.tbl$DEP=="T"])

@@

###  Relevant proteins according to the negative-binomial GLM
nb.tbl <- test.results(nb.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
(nb.nms <- rownames(nb.tbl)[nb.tbl$DEP=="T"])

>>>>

\title{msmsTests package\\
       LC-MS/MS post test filters to improve reproducibility}
\author{Josep Gregori, Alex Sanchez, and Josep Villanueva\\
   Vall Hebron Institute of Oncology \&\\
   Statistics Dept. Barcelona University\\
  \texttt{josep.gregori@gmail.com}}
\date{July 2013}

@@

###  Relevant proteins according to the Poisson GLM
pois.tbl <- test.results(pois.res,e,pData(e)$treat,"U600","U200",div,
                         alpha=alpha.cut,minSpC=SpC.cut,minLFC=lFC.cut,
                         method="BH")$tres
(pois.nms <- rownames(pois.tbl)[pois.tbl$DEP])

@@

###  Relevant proteins according to the quasi-likelihood GLM
ql.tbl <- test.results(ql.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
(ql.nms <- rownames(ql.tbl)[ql.tbl$DEP])

@@

###  Relevant proteins according to the negative-binomial GLM
nb.tbl <- test.results(nb.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
(nb.nms <- rownames(nb.tbl)[nb.tbl$DEP])

### 2013-09-27 inst/doc/msmsTests-Vignette2.Rnw
add hyperref package to 2nd vignette as well
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/msmsTests@79485 bc3139a8-67e5-0310-9ffc-ced21a209358
In function test.results(), DEP column changed to logical
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/msmsTests@80847 bc3139a8-67e5-0310-9ffc-ced21a209358

\title{msmsTests package\\
       Blocks design to compensate batch effects}
\author{Josep Gregori, Alex Sanchez, and Josep Villanueva\\
   Vall Hebron Institute of Oncology \&\\
   Statistics Dept. Barcelona University\\
  \texttt{jgregori@vhio.net}}
\date{July 2013}

@@

<<SubsetFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP=="T"]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql11 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@

@@

<<GlobalFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,gble,pData(gble)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP=="T"]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql22 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@

@@

<<BlockFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,gble,pData(gble)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP=="T"]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql33 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@

>>>>

\title{msmsTests package\\
       Blocks design to compensate batch effects}
\author{Josep Gregori, Alex Sanchez, and Josep Villanueva\\
   Vall Hebron Institute of Oncology \&\\
   Statistics Dept. Barcelona University\\
  \texttt{josep.gregori@gmail.com}}
\date{July 2013}

@@

<<SubsetFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,e,pData(e)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql11 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@

@@

<<GlobalFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,gble,pData(gble)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql22 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@

@@

<<BlockFChunk, echo = TRUE>>=
###  Post-test filter
ql.tbl <- test.results(ql.res,gble,pData(gble)$treat,"U600","U200",div,
                    alpha=0.05,minSpC=2,minLFC=1,method="BH")$tres
ql.nms <- rownames(ql.tbl)[ql.tbl$DEP]
###  Truth table
ridx <- grep("HUMAN",ql.nms)
tp <- length(ridx)
fp <- length(ql.nms)-length(ridx)
(tt.ql33 <- data.frame(TP=tp,FP=fp,TN=ny-fp,FN=nh-tp))
@
